Extended Data

### 2022-02-01 doc/manuscript/Dow_manuscript_Nature.Rmd
small fixes related to R1 comments

Tree-ring records, which can be used to examine relationships of annual growth to temperature but not to understand growth phenology, reveal that growth of temperate deciduous trees tends to be most sensitive to temperature or potential evapotranspiration between late spring and early summer[@dorangeville_drought_2018;@helcoski_growing_2019],
<!-- dorangeville_drought_2018 looks at PET.-->
with some hints that warmer springs may have a modest positive effect on growth[@helcoski_growing_2019].
<!-- add more refs here, but only if already cited elsewhere (to keep n references down-->
Thus, tree-ring evidence does not necessarily align with the finding that warming spring temperatures increase annual forest CO~2~ uptake[@keenan_net_2014].
Characterizing phenological responses of stem growth to warming spring temperatures is critical to bridging this conceptual disconnect and understanding how forest biomass growth is likely to change as the climate warms.

@@

Both MODIS-derived canopy foliage phenology and dendrometer band measurements of stem growth phenology generally shifted backwards as spring temperatures increased (Fig. `r DOY_timing`, `r EDF_pheno_all`). 
We found a consistent effect of temperature ($T_{max}$ or $T_{min}$) throughout the spring, but the strongest effects on stem-growth phenology were found using $T_{max}$ during a critical temperatrue window (CTW). 
CTW was identified by measuring the correlation between all combinations of weekly $T_{max}$ and $DOY_{25}$ from January 1 to mean $DOY_{25}$ for each xylem porosity-site combination (`r EDF_climwin`).
The CTW was defined as the week(s) which had the strongest correlation with $DOY_{25}$.

>>>>

Tree-ring records, which can be used to examine relationships of annual growth to temperature but not to understand growth phenology, reveal that growth of temperate deciduous trees tends to be most sensitive to temperature or potential evapotranspiration between late spring and early summer[@dorangeville_drought_2018;@helcoski_growing_2019]<!-- dorangeville_drought_2018 looks at PET.-->, with some hints that warmer springs may have a modest positive effect on growth[@helcoski_growing_2019].<!-- add more refs here, but only if already cited elsewhere (to keep n references down-->
Thus, tree-ring evidence does not necessarily align with the finding that warming spring temperatures increase annual forest CO~2~ uptake[@keenan_net_2014].
Characterizing phenological responses of stem growth to warming spring temperatures is critical to bridging this conceptual disconnect and understanding how forest biomass growth is likely to change as the climate warms.

@@

Both MODIS-derived canopy foliage phenology and dendrometer band measurements of stem growth phenology generally shifted backwards as spring temperatures increased (Fig. `r DOY_timing`, `r EDF_pheno_all`). 
We found a consistent effect of temperature ($T_{max}$ or $T_{min}$) throughout the spring, but the strongest effects on stem-growth phenology were found using $T_{max}$ during a critical temperature window (CTW). 
CTW was identified by measuring the correlation between all combinations of weekly $T_{max}$ and $DOY_{25}$ from January 1 to mean $DOY_{25}$ for each xylem porosity-site combination (`r EDF_climwin`).
The CTW was defined as the week(s) which had the strongest correlation with $DOY_{25}$.
